---
title: "COD Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

#### Article ID: COGGV
#### Pilot: Cinoo Lee
#### Co-pilot: Tom Hardwicke  
#### Start date: 03/17/2017
#### End date: 03/27/2017  

-------

#### Methods summary: 
Participants were seated in front of the computer screen in the dark and were asked to determine whether the two body positions presented were the same or different (e.g. an arm or a leg of the figure could be in a different angle or in a different position). Half of the time, the person in the picture was in an upright position and half of the time, it was in an inverted position. For each trial, the first stimulus was on the screen for 250 ms, then came a blank screen for 1000ms, and then the second stimulus was presented till participants responded with either the "E" key(i.e. same stimulus) or the "O" key(i.e. different stimulus). Response time and accuracy of the response were recorded.

------

#### Target outcomes: 

"Focus [is] on the findings reported in section 3.1. Across participants accuracy. Specifically, [I will] attempt to reproduce all descriptive and inferential analyses reported in the text below and associated tables/figures:

> Analysis of error rates (Fig. 3) revealed that the inversion effect was strongly reduced when there was no conflict between visual and actual gravity compared to the conditions were there was a conflict of gravity (t(21) = 2.72; p < 0.02; partial eta2 = 0.26).

> The inversion effects were decomposed with Student’s t-test. Analysis revealed that in the conditions with upside down bodies, participants made more errors when gravity orientation was also inverted (gravity conflict, Fig. 1b) than when visual gravity was upright (Fig. 1d) (t(21) = 3.87; p < 0.001; partial eta2 = 0.42). In contrast, we found no differences between the conditions with upright bodies (Fig. 1a and c) (t(21) = 0.35; p = 0.73; partial eta2 = 0.006).
The inversion effect was also computed on RT for conditions with gravity conflict (conditions b–a in Fig. 1) and conditions with- out gravity conflict (conditions d–c in Fig. 1). The normality of data distributions was tested using Kolmogorov-Smirnov test. No distributions differed from normality (all p > 0.05). The inversion effects were compared using Student’s t-tests. The threshold of statistical significance was set at 0.05.

> The reaction time results (Fig. 4) revealed that the inversion effect was also strongly reduced in the condition in which there was no gravity conflict compared to the conditions in which there was a gravity conflict (t(21) = 2.87; p < 0.001; partial eta2 = 0.28). Analysis revealed that in conditions with upside down bodies relative to retinal coordinates, participants were slower when gravity orientation was also inverted (gravity conflict, Fig. 1b) than when visual gravity was upright relative to retinal coordinates (Fig. 1d) (t(21) = 4.10; p < 0.001; partial eta2 = 0.45). In contrast, we found no differences between the conditions with upright bodies (Fig. 1a and c) (t(21) = 0.13; p = 0.89; partial eta2 = 0.001)."

Additional data analysis notes:
"For RT data, we analyzed only trials that corresponded to a correct response: 7468 ± 506 trials over 8448 (88.4%). When reaction time was slower than 200 ms or when it deviated from the mean by more or by less than 3 standard deviations, the trial was excluded (0.5% of the data)."
"The inversion effect was calculated by the subtraction of the error rate measured in upright orientation from the error rate in inverted orientation ( 180 ) for each pair. This was calculated for conditions with gravity conflict (b-a conditions in Fig. 1) and conditions without gravity conflict (d-c conditions in Fig. 1). The inversion effects were compared using Student’s t-test. The threshold of statistical significance was set at 0.05. When needed, a Bon- ferroni correction for multiple comparisons was used. In this case, the corrected threshold of statistical significance was a = 0.025 (0.05/2)."

------
```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages
```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(CODreports) # custom report functions
```

## Step 2: Load data

```{r}
expdata <- read_excel("~/Documents/Classes/Winter2017/PSYC254/Pset3/set_COGGV/data/data.xlsx", sheet = 2)
summary(expdata)

expdata <- expdata %>%
  rename(id = Subject_nb)

names(expdata) <- gsub(" ", "_", names(expdata))
```

## Step 3: Tidy data
```{r}
expdata_tidy <- select(expdata, id, starts_with("B"))
expdata_tidy <- expdata_tidy %>%
  rename(BUGD = BU_GD,
         BDGU = BD_GU,
         BUGU = BU_GU,
         BDGD = BD_GD,
         BUGD_ms = `BU_GD_(ms)`,
         BDGU_ms = `BD_GU_(ms)`,
         BUGU_ms = `BU_GU_(ms)`,
         BDGD_ms = `BD_GD_(ms)`)

expdata_accuracy <- expdata_tidy %>%
  select(id, BUGD, BDGU, BUGU, BDGD) %>%
  gather(position, accuracy, BUGD, BDGU, BUGU, BDGD)

expdata_accuracy <- expdata_accuracy %>%
  mutate(body = substr(expdata_accuracy$position,2,2)) %>%
  mutate(gravity = substr(expdata_accuracy$position,4,4)) %>%
  select(id, body, gravity, accuracy)
         
  expdata_rt <- expdata_tidy %>%
  select(BUGD_ms, BDGU_ms, BUGU_ms, BDGD_ms) %>%
  rename(BUGD = BUGD_ms,
         BDGU = BDGU_ms,          
         BUGU = BUGU_ms,
         BDGD = BDGD_ms) %>%
  gather(rtposition, rt, BUGD, BDGU, BUGU, BDGD)
  
  expdata_rt <- expdata_rt %>%
  mutate(body = substr(expdata_rt$rtposition,2,2)) %>%
  mutate(gravity = substr(expdata_rt$rtposition,4,4)) %>%
  select(rt)

expdata_tidy <- bind_cols(expdata_accuracy, expdata_rt) %>%
  select(id, body, gravity, accuracy, rt)

expdata_tidy <- expdata_tidy %>%  
mutate(subid = substr(expdata_tidy$id,2,4)) %>%
  select(subid, body, gravity, accuracy, rt)

expdata_tidy <- expdata_tidy %>%
  rename(id = subid)
```

## Step 4: Run analysis

### Pre-processing

```{r}
summary(expdata_tidy)
mean(expdata_tidy$rt) #786.15
sd(expdata_tidy$rt) #335.58
expdata_tidy$body = factor(expdata_tidy$body)
expdata_tidy$gravity = factor(expdata_tidy$gravity)

error_analysis <- expdata_tidy %>%
  select(id, body, gravity, accuracy)

#Only trials that corresponded to a correct response
#Excluded reaction time slower than 200 ms or rt deviating from the mean by more or by less than 3 standard deviations
rt_analysis <- expdata_tidy %>%
   filter(!(is.na(rt)) & accuracy == 1 & rt > 200 & rt < 1792)
```

### Descriptive statistics

```{r}
summary(rt_analysis)
sd(rt_analysis$rt) # Standard deviation
summary(error_analysis)

sem <- function(x) {sd(x) / sqrt(length(x))}

ci95.norm <- function(x) {
  me <- sem(x)*qnorm(.975)
  c(mean(x)-me, mean(x)+me)
}
```

### Inferential statistics
"The inversion effect was calculated by the subtraction of the error rate measured in upright orientation from the error rate in inverted orientation (180) for each pair. This was calculated for conditions with gravity conflict (b-a conditions in Fig. 1) and conditions without gravity conflict (d-c conditions in Fig. 1). The inversion effects were compared using Student’s t-test. The threshold of statistical significance was set at 0.05. When needed, a Bonferroni correction for multiple comparisons was used. In this case, the corrected threshold of statistical significance was a = 0.025 (0.05/2)."

> Analysis of error rates (Fig. 3) revealed that the inversion effect was strongly reduced when there was no conflict between visual and actual gravity compared to the conditions were there was a conflict of gravity (t(21) = 2.72; p < 0.02; partial eta2 = 0.26).

> The inversion effects were decomposed with Student’s t-test. Analysis revealed that in the conditions with upside down bodies, participants made more errors when gravity orientation was also inverted (gravity conflict, Fig. 1b) than when visual gravity was upright (Fig. 1d) (t(21) = 3.87; p < 0.001; partial eta2 = 0.42). In contrast, we found no differences between the conditions with upright bodies (Fig. 1a and c) (t(21) = 0.35; p = 0.73; partial eta2 = 0.006).
The inversion effect was also computed on RT for conditions with gravity conflict (conditions b–a in Fig. 1) and conditions with- out gravity conflict (conditions d–c in Fig. 1). The normality of data distributions was tested using Kolmogorov-Smirnov test. No distributions differed from normality (all p > 0.05). The inversion effects were compared using Student’s t-tests. The threshold of statistical significance was set at

```{r}
#Error Rate
means_ud <- error_analysis %>%
  filter(body == "U", gravity == "D") %>%
  filter(!is.na(accuracy)) %>%
  group_by(id) %>%
  summarise(ud_accu_mean = mean(accuracy))

means_du <- error_analysis %>%
  filter(body == "D", gravity == "U") %>%
  filter(!is.na(accuracy)) %>%
  group_by(id) %>%
  summarise(du_accu_mean = mean(accuracy)) %>%
  rename(idd = id)

means_uu <- error_analysis %>%
  filter(body == "U", gravity == "U") %>%
  filter(!is.na(accuracy)) %>%
  group_by(id) %>%
  summarise(uu_accu_mean = mean(accuracy)) %>%
  rename(iddd = id)

means_dd <- error_analysis %>%
  filter(body == "D", gravity == "D") %>%
  filter(!is.na(accuracy)) %>%
  group_by(id) %>%
  summarise(dd_accu_mean = mean(accuracy)) %>%
  rename(idddd = id)

means_bodyud <- bind_cols(means_ud, means_du, means_uu, means_dd) %>%
  select(id, ud_accu_mean, du_accu_mean, uu_accu_mean, dd_accu_mean) %>%
  mutate(inversion_effect = ud_accu_mean - du_accu_mean, dd_accu_mean - uu_accu_mean)

means <- error_analysis %>%
  group_by(body, gravity, id) %>%
  summarise(accuracy = mean(accuracy)) %>%
  ungroup() %>%
  mutate(body_gravity = paste(body, gravity, sep='')) %>%
  select(-body, -gravity) %>%
  spread(body_gravity, accuracy) %>%
  mutate(yes_conflict = UD - DU,
         no_conflict = DD - UU)

t.test(means$yes_conflict, means$no_conflict, paired = TRUE)
```

## Step 5: Conclusion

```{r}
```

[Please also include a brief text summary describing your findings. If this reproducibility check was a failure, you should note any suggestions as to what you think the likely cause(s) might be.]

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
